Modeling vertical-axis cross-flow turbine wakes

### 2015-07-20 paper.tex
Add todonote

The computational domain is a rectangular volume

\todo[inline]{Add domain extent in terms of turbine diameter.}

 with a cylindrical sliding mesh
interface, where the turbine zone rotates at a mean tip speed ratio
$\lambda=1.9$ with an unsteadiness as the blade passage frequency specified to
mimic the experimental data. The 2-D mesh is shown in Figure~\ref{fig:mesh}.

>>>>

The computational domain is a rectangular volume
\todo[inline]{Add domain extent in terms of turbine diameter.}
with a cylindrical sliding mesh interface, where the turbine zone rotates at a
mean tip speed ratio $\lambda=1.9$ with a sinusoidal fluctuation at the blade
passage frequency specified to mimic the experimental data. 
\todo[inline]{Get parameters of TSR unsteadiness.}
The 2-D mesh is
shown in Figure~\ref{fig:mesh}.
